% what kind of conclusion do you want to get?? My method works in some cases while other methods can not. 
% <1> deal with some situations
% <2> improve precision and accuracy compared to existing model
% Further work:<1> consider multiple KPIs in the model and adjust them
%    <2> Add long-term dependency directly on Petri net
%    <3> deal with the unsound model and fix them in some way
%    <4> simply using the threshold to generate model, but want to integrate with machine learning and generate good model

% Also, some limitations about our methods, we need to point them out.
%% can not give out the best setting
%% it is absoulte values, not vary due to the problem.
In this thesis, we explore ways to use negative information in model repair and propose our innovative method. Firstly, we analyzed the current techniques of model repairs based on performance and detected their shortcomings. Then we  proposed a general framework to incorporate the forces from the existing model, positive and negative event logs. Three abstraction data models in the same type are built to represent those forces. Later, forces are balanced based on those data models and expressed in a new data model. From this new data model, process models are discovered and converted into repaired models with the required type. Optional post processes include long-term dependency detection and silent transition reduction, which further improve the repaired models. 

Moreover, we demonstrate the usage of our method by conducting experiments with synthetic data and real life data. In the situations shown with synthetic data,  our method is able to overcome the shortcomings of the current repair techniques and provide repaired models with higher accuracy and precision. In experiments with the real life data, it shows that the proposed techniques are capable to produce models which better quality measurements while keeping the similarity between the repaired and reference models. Additionally, with respect to other methods, it runs faster and generates simpler models. 

As future work, we consider improving the rules of balancing different forces, which choose the directly-follows relation on the simple subtraction and sum of those forces. Advanced data mining techniques such as association rules discovery, can be used on those forces to derive rules for building a process model. The same improvement can be applied on the long-term dependency discovery. Moreover, in this thesis, the long-term dependency discovery is restricted on the activities with exclusive choice relations. Later, we can extend the long-term dependencies on other possible relations. Also, we can discard the process tree as our intermediate result and detect long-term dependencies directly on the Petri net. 

In conclusion, our proposed repair method is able to incorporate negative instances with the existing model and positive instances, which provides an innovative way to repair models in Process Enhancement. 
